\paragraph{The problem of continuity} The problem is that often inexperienced students are elected into the USG and secondly, that the experience of the previous members is hardly passed on to the new ones. This, leads to the USG working on the same issues over and over again, without learning from previous attempts. As pointed out in the handbook the student body (including the USG) has a collective memory of at most 18 month.

This was the reason to have the elections at the end of the semesters and to invite the newly elected as a standing guest for the remaining semester, before putting them into office officially. While improving the situation, the problem is still present. Furthermore, the new chair of a committee might be amongst the least experienced members of the committee when elected. 

\paragraph{Unfamiliarity with the USG procedures} Up until now, a vast majority of elected USG members had no previous experience in the USG and were not familiar with the rules and procedures in the USG when elected. Furthermore, the new chair of committee should be familiar with the procedures and customs of the committee.  Particularly, the chairs of a committee should be previous members of that committee and accepted amongst the members of the committee.

\paragraph{The right of the committees to have a say in the choice of their chair}
Currently, the current members of a committee have no say in the election of their chair. This, is suboptimal for various reasons: \begin{itemize}
	\item The chair is not accustomed with the workings of the committee. 
	\item The chair might not know the other members before coming into office, limiting them ability to chair the committee meetings. 
	\item The committee members can judge the strength and weaknesses of the other members they worked with. Their experience is neglected in the process of selecting a new chair.
\end{itemize}

\paragraph{Equal representation of committees in the parliament}
It is important that all committee's interests (after all the actors in the USG with most manpower which do most of the work) are well represented in the parliament and to ensure a good cooperation between the parliament and the committees. Also different committees can have different interests and it is important that they are all as equally as possible represented in the parliament. 

\paragraph{Inflexibility of the election system}
Currently, Collage representatives are allowed only to chair the CAC, Focus area representatives are only allowed to chair the AAC and only the treasurer is allowed to chair the FAC. This way if a member of a USG committee wants to run for an elected office to chair them committee, they can only run in the Fall semester to chair the FAC or AAC and only in Spring to chair the CAC. However, forcing committed committee members running in an election to chair a different committee, leads to the above problems. Therefore, committee members running in an election to (co)-chair their committee are currently unnecessarily restricts from running. 