The idea is to elect the members of parliament from current USG members and to allow the committees to decide on their own chair. 
In practice the Members of Parliament and Committee chairs would be chosen as follows. 

At the end of each semester, candidates from the USG can run as candidates for members of parliament. Additionally each USG member can decide to run for the position of the (vice)-president in the Fall/Spring semester respectively. These candidates are then voted on by the student body and the $n$ candidates with most votes form the newly elected members of parliament (where $n$ denotes the number of committees in the USG). Additionally, the (vice)-president is elected. Amongst the elected candidates from each committee, the committee may elect its (co)-chair (requires the parliaments approval). Alternatively, or if no candidate from the committee got elected, either the committee may decide on a chair amongst its non-elected members (requires the parliament's approval) or the committee may accept a different member of parliament as a (co)-chair (requires the committee's approval). In the first case the chair of the committee is invited as a standing guest to the parliament and granted the same rights as a member of parliament, but with voting power limited to decision in the responsibility of the committee, in order to properly represent the committee to the parliament. If no co-chair is elected the previous chair (if not eligible, the previous co-chair) becomes the new co-chair by default.

In case parliament and committees can't agree on chairs for a committee, the parliament can decision on the chair (one of the members of parliament) with a 2/3 majority of members including the president. The committee, can reject this decision with an absolute 2/3 majority, in this case an election by the USB between the candidate from the committee and from the parliament is carried out to decide the issue. 

Each USG member may have at most one (co)-chair position in a committee.